An Accurate Model for SARS-CoV-2 pooled RT-PCR Tests Errors

### 2021-03-16 comment.tex
More words

To summarize, we assume that for a single pool, a positive test result
is generated in one of two paths. Either, SARS-CoV-2 RNA from an
infected individual's sample is correctly amplified and detected, and
this can happen for each positive sample in a pool. Or, some erroneous
amplification occurs (e.g. contaminant viral RNA is introduced), an
event that occurs at most once per pool. Our model is illustrated in
Figure~\ref{fig:likelihood}, and explicitly defined below.

A negative pooled test result occurs when all detection paths (both
correct and erroneous) fail. The probability of no false-detection
accounts for the $\spec$ term. The probability of no correct detection
is $(1-\sens)$ per infected individual. The probability that all such
paths fail is the product of the above mentioned terms, displayed in
\eqref{eq:likelihood a}.%%  The probability of a positive result,
%% presented in \eqref{eq:likelihood b}, is simply the complement.
%% The probability of a negative pooled test result is presented in
%% \eqref{eq:likelihood a} (along with its complement
%% \eqref{eq:likelihood b}), and explained below.
%\begin{subequations}
\begin{align}%\label{eq:single likelihood}
  %\begin{split}
    \Pr(\data=0 | \theta) &= \spec\prod_{i=1}^N
    (1-\sens)^{\theta_i} = \spec(1-\Se)^{\sum\theta_i}, \label{eq:likelihood a}
    %
    %
    %
    %% \Pr(\data=1 | \theta) &= 1 - \spec\prod_{i=1}^N
    %% (1-\sens)^{\theta_i} = 1 - \spec(1-\Se)^{\sum\theta_i} . \label{eq:likelihood b}
  %\end{split}
\end{align}
%\end{subequations}
%% Combining \eqref{eq:likelihood a} and \eqref{eq:likelihood b}, and
%% recalling that $\data \in \{0,1\}$ yields:

>>>>

To summarize, we assume that for a single pool, a positive test result
is generated in one of two paths. Either, SARS-CoV-2 RNA from an
infected individual's sample is correctly amplified and detected, and
this can happen for each positive sample in a pool, with probability
$\Se$. Or, some erroneous amplification occurs (e.g. contaminant viral
RNA is introduced), an event that occurs at most once per pool, with
probability $1-\Sp$. Our model is illustrated in
Figure~\ref{fig:likelihood}, and summarized in
%% A negative pooled test result occurs when all detection paths (both
%% correct and erroneous) fail. The probability of no false-detection
%% accounts for the $\spec$ term. The probability of no correct detection
%% is $(1-\sens)$ per infected individual. The probability that all such
%% paths fail is the product of the above mentioned terms, displayed in
\eqref{eq:likelihood a}.%%  The probability of a positive result,
%% presented in \eqref{eq:likelihood b}, is simply the complement.
%% The probability of a negative pooled test result is presented in
%% \eqref{eq:likelihood a} (along with its complement
%% \eqref{eq:likelihood b}), and explained below.
%\begin{subequations}
\begin{align}%\label{eq:single likelihood}
  %\begin{split}
    \Pr(\data=0 | \theta) &= \spec\prod_{i=1}^N
    (1-\sens)^{\theta_i} = \spec(1-\Se)^{\sum\theta_i}. \label{eq:likelihood a}
    %
    %
    %
    %% \Pr(\data=1 | \theta) &= 1 - \spec\prod_{i=1}^N
    %% (1-\sens)^{\theta_i} = 1 - \spec(1-\Se)^{\sum\theta_i} . \label{eq:likelihood b}
  %\end{split}
\end{align}
%\end{subequations}
%% Combining \eqref{eq:likelihood a} and \eqref{eq:likelihood b}, and
%% recalling that $\data \in \{0,1\}$ yields:
